Testing and Isolation Efficacy; Insights from a Simple Epidemic Model

### 2021-01-25 SIR_manuscript.tex
Just a couple minor changes before an interruption

The observed dynamics of the COVID-19 epidemic are driven by both epidemiological processes (infection and recovery) and testing processes (testing and test reporting). In addition to determining what we actually observe about the epidemic (case reports), testing processes can also feed back to affect the epidemiological dynamics through isolation and quarantine. Specifically, individuals who are awaiting the results of a test may partially or fully self-isolate, and individuals who have tested positive are highly likely to self-isolate. We developed a model that incorporates mechanistic epidemic processes and testing in order to explore the effects of testing and isolation on epidemic dynamics.

>>>>

The observed dynamics of the COVID-19 epidemic are driven by both epidemiological processes (infection and recovery) and testing processes (testing and test reporting). In addition to shaping epidemic observations (via case reports), testing processes can also affect epidemiological dynamics. In particular, individuals who are awaiting the results of a test may partially or fully self-isolate, and individuals who have tested positive are highly likely to self-isolate. We developed a model that incorporates mechanistic epidemic processes and testing in order to explore the effects of testing and isolation on epidemic dynamics.
